### 2022-05-18 manuscript.Rmd
Format paragraphs as one line of code
Re-format probabilities > 99.9%
Add references for effect size conversion

For our first meta-analytic model, effect sizes were quantified as the standardized mean difference in infants' looking times for novel and familiar rotated objects. Using this effect size index, we ran a Bayesian three-level random-effects model to test if there was evidence that infants did perform mental rotation. Across studies, infants indeed looked longer at novel rotated objects than at familiar rotated objects, with a standardized mean difference of $g = `r summ_meta$intercept`$, 95% credible interval (CrI) [`r summ_meta$intercept.lower`, `r summ_meta$intercept.upper`] (Fig.\ \@ref(fig:fig1)). The probability for this effect being greater than zero was $\approx$ `r print_prob(hyp_meta$Post.Prob)`. The heterogeneity of effect sizes was $\sigma_{\text{experiment}}^2 = `r summ_meta$sigma2_experiment`$, 95% CrI [`r summ_meta$sigma2_experiment.lower`, `r summ_meta$sigma2_experiment.upper`], at the experiment level and $\sigma_{\text{article}}^2 = `r summ_meta$sigma2_article`$, 95% CrI [`r summ_meta$sigma2_article.lower`, `r summ_meta$sigma2_article.upper`] at the article level. Therefore, `r print_perc(1 - summ_meta$icc)` of the heterogeneity between effect sizes was attributable to differences between experiments *within* articles and `r print_perc(summ_meta$icc)` was attributable to differences *between* articles.

@@

For the meta-analysis of mental rotation performance, one outcome measure per experiment was converted into a standardized mean difference with small sample correction (Hedges' $g$) using the formulas provided in Supplementary Table\ \@ref(tab:tabs5). The standard error of Hedges' $g$ for each experiment was computed using the formula provided by @goulet-pelletier2018: $${SE}_\text{rotation}=\sqrt{\frac{{df}}{{df}-2}\frac{2(1-r)}{n}\left(1+g_\text{rotation}^2\frac{n}{2(1-r)}\right)-\frac{g_\text{rotation}^2}{J({df})^2}}$$ where $n$ is the sample size of the experiment, ${df}$ are the degrees of freedom (with ${df} = 2(n-1)$), $r$ is the correlation between the two dependent measures in the experiment, and $J({df})$ is the correction factor for small samples as described in row (1) of Supplementary Table\ \@ref(tab:tabs5). The correlation $r$ was not reported in any of the original articles [@harrer2021]. We therefore always assumed a correlation of $r = 0.50$ to make our analysis comparable to standard (between-group) meta-analyses [@cohen1988; @lakens2013; @morris2002] and because we were able to infer an average correlation of $r \approx 0.50$ from a subsample of articles which provided sufficient information (Supplementary Methods 1). A sensitivity analysis indicated that changing the assumed correlation to values from $r = -0.90$ via $r = 0.00$ to $r = 0.90$ had no meaningful impact on the meta-analytic effect sizes (Supplementary Tables\ \@ref(tab:tabs7) and\ \@ref(tab:tabs8)).

>>>>

For our first meta-analytic model, effect sizes were quantified as the standardized mean difference in infants' looking times for novel and familiar rotated objects. Using this effect size index, we ran a Bayesian three-level random-effects model to test if there was evidence that infants did perform mental rotation. Across studies, infants indeed looked longer at novel rotated objects than at familiar rotated objects, with a standardized mean difference of $g = `r summ_meta$intercept`$, 95% credible interval (CrI) [`r summ_meta$intercept.lower`, `r summ_meta$intercept.upper`] (Fig.\ \@ref(fig:fig1)). The probability for this effect being greater than zero was `r print_prob(hyp_meta$Post.Prob)`. The heterogeneity of effect sizes was $\sigma_{\text{experiment}}^2 = `r summ_meta$sigma2_experiment`$, 95% CrI [`r summ_meta$sigma2_experiment.lower`, `r summ_meta$sigma2_experiment.upper`], at the experiment level and $\sigma_{\text{article}}^2 = `r summ_meta$sigma2_article`$, 95% CrI [`r summ_meta$sigma2_article.lower`, `r summ_meta$sigma2_article.upper`] at the article level. Therefore, `r print_perc(1 - summ_meta$icc)` of the heterogeneity between effect sizes was attributable to differences between experiments *within* articles and `r print_perc(summ_meta$icc)` was attributable to differences *between* articles.

@@

For the meta-analysis of mental rotation performance, one outcome measure per experiment was converted into a standardized mean difference with small sample correction (Hedges' $g$) using the formulas provided in Supplementary Table\ \@ref(tab:tabs5) [@goulet-pelletier2018; @hedges1985; @lakens2013; @rosenthal1991; @cumming2012]. The standard error of Hedges' $g$ for each experiment was computed using the formula provided by @goulet-pelletier2018: $${SE}_\text{rotation}=\sqrt{\frac{{df}}{{df}-2}\frac{2(1-r)}{n}\left(1+g_\text{rotation}^2\frac{n}{2(1-r)}\right)-\frac{g_\text{rotation}^2}{J({df})^2}}$$ where $n$ is the sample size of the experiment, ${df}$ are the degrees of freedom (with ${df} = 2(n-1)$), $r$ is the correlation between the two dependent measures in the experiment, and $J({df})$ is the correction factor for small samples as described in row (1) of Supplementary Table\ \@ref(tab:tabs5). The correlation $r$ was not reported in any of the original articles [@harrer2021]. We therefore always assumed a correlation of $r = 0.50$ to make our analysis comparable to standard (between-group) meta-analyses [@cohen1988; @lakens2013; @morris2002] and because we were able to infer an average correlation of $r \approx 0.50$ from a subsample of articles which provided sufficient information (Supplementary Methods 1). A sensitivity analysis indicated that changing the assumed correlation to values from $r = -0.90$ via $r = 0.00$ to $r = 0.90$ had no meaningful impact on the meta-analytic effect sizes (Supplementary Tables\ \@ref(tab:tabs7) and\ \@ref(tab:tabs8)).
